\begin{center}
	\textbf{\Large Declaration}
\end{center}

I, \textbf{[Your Full Name]}, hereby declare that the work presented in this \textit{project} entitled ``\textit{[Title of Your Work]}'' is entirely my own. The content of this \textit{ project} has been generated through my independent efforts, research, and scholarly contributions. I further declare that:
\begin{enumerate}
	\item \textbf{Originality:}
	\begin{itemize}
		\item The ideas, concepts, and contributions presented in this work are solely the result of my own intellectual endeavours.
	\end{itemize}
		\item \textbf{Authenticity:}
	\begin{itemize}
		\item All data, figures, tables, and findings presented in this \textit{project}are genuine and have not been fabricated or manipulated.
	\end{itemize}
		\item \textbf{No Use of AI Tools:}
	\begin{itemize}
		\item I have not used any AI-based tools to generate significant portions of this \textit{ project} including but not limited to content, research objectives, hypotheses, and analysis.
	\end{itemize}
		\item \textbf{No Plagiarism:}
	\begin{itemize}
		\item I have properly cited and referenced all external sources and works consulted during the preparation of this \textit{[thesis/dissertation/research project]}.
		\item There is no instance of plagiarism or unauthorized use of others' intellectual property.
	\end{itemize}
		\item \textbf{Independent Work:}
	\begin{itemize}
		\item This work has been conducted independently, without any collaboration or assistance that would compromise the originality of the content.
	\end{itemize}
		\item \textbf{Academic Integrity:}
	\begin{itemize}
		\item I have adhered to the principles of academic integrity and ethical research throughout the entire process of producing this \textit{[thesis/dissertation/research project]}.
	\end{itemize}
\end{enumerate}
I understand the consequences of academic dishonesty and affirm that this declaration accurately reflects the nature and authenticity of my work.
\begin{flushright}
	\textbf{Date:} \textit{[Date of Submission]}
\end{flushright}
\begin{flushright}
	\textbf{Signature:} \underline{\hspace{5cm}} \\
	\textit{[Your Full Name]}
\end{flushright}